Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-12 paper/main.tex
backing up progress on results section...

@@

- when lists are sorted by a given feature, how is memory performance affected (relative to feature rich -- early lists only)?
  - do some order manipulations matter more than others?  e.g. compare semantic vs. lexicographic vs. visual -- early lists only

- are order effects "sticky"?
  - when *early* lists are sorted by a given feature, how is memory performance on *late* lists affected (relative to feature rich -- late lists only)?
  - do some order manipulations matter more than others?  e.g. compare semantic vs. lexicographic vs. visual -- late lists only

  - compare behavior on early vs. late lists for order manipulation condition
    - does feature clustering on early lists correlate with recall on early (or late) lists?
    - does feature clustering on late lists correlate with recall on early (or late) lists?
    - (ditto, but replace "recall" with "temporal clustering")

- for feature-rich lists, do order effects matter?
  - recall + dynamics + organization on order-manipulation conditions vs. feature rich
  - fingerprint trajectories: how much do fingerprints change over time, are they sensitive to order manipulations?

- are fingerprints maleable?  how does match between fingerprint + presentation order affect recall performance (adaptive conditions)?

>>>>

%%%%%
% - next paragraph: relative strengths of order manipulations (compare order manipulations to *other order manipulations* instead of feature rich)

% - and then, another paragraph: stickiness-- compare results on late lists (order manip vs. feature rich, order manip vs. other order manip).

% - the key: individual differences.  some participants are more affected by order manips than others.  for those participants, order manips are sticky and affect recall behavior more.
%   - one subtlety: explain fig 5 and 7 scatterplots (and inlays)-- some *conditions* are overall more affective; pattern is more complicated than can be identified with pairwise comparisons
%   - implication re: individual diffs: adaptive condition-- stabilize should improve performance, destabilize should worsen performance

@@

% - are order effects "sticky"?
%   - when *early* lists are sorted by a given feature, how is memory performance on *late* lists affected (relative to feature rich -- late lists only)?
%   - do some order manipulations matter more than others?  e.g. compare semantic vs. lexicographic vs. visual -- late lists only

%   - compare behavior on early vs. late lists for order manipulation condition
%     - does feature clustering on early lists correlate with recall on early (or late) lists?
%     - does feature clustering on late lists correlate with recall on early (or late) lists?
%     - (ditto, but replace "recall" with "temporal clustering")

% - for feature-rich lists, do order effects matter?
%   - recall + dynamics + organization on order-manipulation conditions vs. feature rich
%   - fingerprint trajectories: how much do fingerprints change over time, are they sensitive to order manipulations?

% - are fingerprints maleable?  how does match between fingerprint + presentation order affect recall performance (adaptive conditions)?
